Title here \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2022-12-13 manuscript/manuscript.tex
started writing a bit about the models

% !TeX program = pdfLaTeX
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

@@

@@

% Text with citations by \cite{Galyardt14mmm}.
In this section we first review two well-established techniques commonly used in sustainable fishery management. 
These are the maximum sustainable yield (MSY) and the constant escapement (CE) approaches. 
After this, reinforcement learning is briefly reviewed

@@

\hypertarget{sec:3}{%
\subsection{Reinforcement learning}\label{sec:rl}}

\hypertarget{sec:4}{%
\section{A three-species dynamical model}\label{sec:model}}

>>>>

% !TeX program = pdfLaTeX
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

@@

\def \der #1 #2 {\frac{\mathrm{d}#1}{\mathrm{d}#2}}

@@

% Text with citations by \cite{Galyardt14mmm}.
In this section we first review two well-established techniques commonly used in sustainable fishery management. 
These are the maximum sustainable yield (MSY) and the constant escapement (CE) approaches. 
After this, deep reinforcement learning is briefly reviewed

@@

\hypertarget{sec:3}{%
\subsection{Deep reinforcement learning}\label{sec:rl}}

\hypertarget{sec:4}{%
\section{A hierarchy of dynamical models}\label{sec:model}}

In this section we present three models of increasing complexity which plausibly describe the population dynamics of a marine ecosystem.
These models will form the test beds for the comparison between classical fishery management strategies and DRL.

\hypertarget{paragraph-headings}{%
\paragraph{A one-dimensional tipping point model.}\label{p:may}}
Our first model has been used in~\cite{may77} to study the possible dangers of driving a dynamical ecosystem past a tipping point.
Its dynamics is given by
\begin{align}
  \label{eq:may77}
  \der{V} t = rV\left(
    1-V/K
    \right) 
    -
    \frac{\beta H V^2}{V_0^2 + V^2}. 
\end{align}
Here the only dynamic degree of freedom is $V$, while $r,\ K,\ \beta,\ V_0,$ and $H$ are fixed parameters.
This model describes a population $V$ which grows logistically up to a carrying capacity of $K$, and whose growth is controlled by a constant population $H$ of predators.
For fixed values of $r,\ K,\ V_0$ and $\beta$, varying $H$ may produce a \emph{catastrophe} (see Fig.~\ref{fig:tbd}).
